Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
umberto: comment Section 4
added right table with new SOAP2.0 data

\author{U. Simola \inst{1,2}
	    \thanks{\email{umberto.simola@yale.edu}}
	    \and X. Dumusque\inst{3}
	    \thanks{Branco Weiss Fellow--Society in Science (url: \url{http://www.society-in-science.org})}    
	    \and Jessi Cisewski\inst{2}
	    }

@@

The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the skewness (i.e. the asymmetry) of the distribution. Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $y\in Y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right),
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}.
The skewness parameter $\alpha$ quantifies the asymmetry of the SN. 
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.  A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\ref{def:snd_gen}. If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density of a Normal distribution. Note that $\Phi(0) = 0.5$ because $\Phi(0)$ is the the probability that a standard Normal random variable is less than or equal than 0.}.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
   \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types. Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
   \label{fig:SN.plot}
\end{figure}
%
For reasons related to the interpretation of the parameters in Eq.~\ref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).  This CP is much closer to the parametrization of a Normal distribution, as it uses a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$. In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of $(\xi, \omega^2, \alpha)$. This can be done using the following relations:
%
\begin{equation} \label{eq:snd_cp}
\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
\end{equation}
%
where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$ \citep[e.g.][]{Arellano-2010}.

@@

Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficiency in the case of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
It is straightforward to see that the proposed correction for \xavier{stellar activity is able to account for the majority of the activity signal created by a faculae, with a $R^2$ of our model larger than 0.95. In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
We see a slightly smaller rms after correction for the SN parameters, however the different is not significant. When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used, i.e. a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2. Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the intercept $\beta_0$ is only significant at a level of 1\% in the case of the Normal parameters, the coefficient $\beta_3$ that corresponds to the CCF width is only significant when using the SN parameters, and the coefficient $\beta_4$ that account for the interaction between the width and the asymmetry parameters is never significant.}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:faculae.correction}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.0016$    & $0.26$ & $0.60$ \\
\hline
$\beta_{1}$            &    $3.75e-05$    & $0.0068$ & $0.0069$ \\
\hline
$\beta_{2}$            &     $7.79e-16$   &  $1.97e-05$ & $3.69e-08$\\
\hline
$\beta_{3}$            &     $0.25$   &  $0.0011$ & $0.0011$\\
\hline
$\beta_{4}$            &     $0.53$   &  $0.21$ & $0.21$\\
\hline
$R^{2}$      &     $0.9967$    &  $0.9571$ & $0.977$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\ref{eq:RV:correction}. Beyond the contrast parameter A and the asymmetry parameter of the CCF which are useful for both the analyses, the width of the CCF is statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses. The term of interaction between the asymmetry and the width of the CCF is not helpful to explain part of the variability in the set of RV's. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
\label{table:faculae.test}
\end{table}

@@

As before, we corrected the originally RVs by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.98. \xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms. In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant. When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.

In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, we observe that the intercept and $\beta_3$, corresponding to the width of the CCF, are useless to understand the variation seen in RVs. This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}. We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:spot.correction}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.47$    & $0.84$ & $0.81$ \\
\hline
$\beta_{1}$            &    $0.00035$    & $0.064$ & $0.064$ \\
\hline
$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.53$   &  $0.61$ & $0.61$\\
\hline
$\beta_{4}$            &     $1.11e-07 $   &  $2.85e-08 $ & $ 2.87e-08 $\\
\hline
$R^{2}$      &     $0.9897$    &  $0.9914$ & $0.9929$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}. All the covariates are statistically useful to explain the variability in RV's causued by a spot except the intercept and the width of the CCF. Concerning the SN analysis, the contrast parameter A is not statistically significant at level $5\%$. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
\label{table:spot.test}
\end{table}

@@

In order to correct the RVs from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet. The observed RV can therefore be modeled by a combination of the activity and the planet signal:}
%
\begin{equation}
RV= RV_{\text{stellar activity}} + RV_{\text{planet}},
\label{eq:RV:correction.overall}
\end{equation}
%
\xavier{where $RV_{\text{stellar activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:}
%
\begin{equation}
RV_{\text{exoplanet}}= K \sin \left(\frac{2 \pi}{P} (t - t_{0})\right),
\label{eq:RV:correction.planet}
\end{equation}
%
where the amplitude $K$, the orbital period $P$ and the epoch at the periapsis $t_{0}$ are three unknown parameters that define the planetary orbit.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $7.09e-09$    & $ 3.44e-07$  & $4.96e-09$ \\
\hline
$\beta_{1}$            &    $0.00105$    & $0.0052$  & $0.0052$ \\
\hline
$\beta_{2}$            &     $2e-16$   & $2.43e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.79$   &  $0.22$  & $0.22$\\
\hline
$\beta_{4}$            &     $6.73e-07$   &  $7.78e-06$ & $7.82e-06$\\
\hline
K            &     $2e-16$   &  $2e-16$   & $ 2e-16 $\\
\hline
P            &     $2e-16$   &  $2e-16$ & $2e-16 $\\
\hline
$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16 $\\
\hline
$\text{Residuals}$      &     $0.61 \ms$    &  $ 0.60 \ms$ & $0.60 \ms$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\ref{eq:RV:correction.overall}. All the parameters are statistically helpful to address spurious variations in RV's except the FWHM. Concerning the keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet. Note that since non linear least squares are required, the residual standard error rather than the $R^2$ is displayed for each case.}
\label{table:spotplanet.test}
\end{table}

@@

>>>>

\author{U. Simola \inst{1,2}
	    \thanks{\email{umberto.simola@helsinki.fi}}
	    \and X. Dumusque\inst{3}
	    \thanks{Branco Weiss Fellow--Society in Science (url: \url{http://www.society-in-science.org})}    
	    \and Jessi Cisewski\inst{2}
	    }

@@

The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the skewness (i.e. the asymmetry) of the distribution. Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $y\in Y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right),
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}.
The skewness parameter $\alpha$ quantifies the asymmetry of the SN. 
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.  A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\ref{def:snd_gen}. If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density of a Normal distribution. Note that $\Phi(0) = 0.5$ because $\Phi(0)$ is the the probability that a standard Normal random variable is less than or equal than 0.}.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 2.3in]{Skew_Normal_densities_jjck.pdf} 
   \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types. Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
   \label{fig:SN.plot}
\end{figure}
%
For reasons related to the interpretation of the parameters in Eq.~\ref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).  This CP is much closer to the parametrization of a Normal distribution, as it uses a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$. In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of $(\xi, \omega^2, \alpha)$. This can be done using the following relations:
%
\begin{equation} \label{eq:snd_cp}
\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
\end{equation}
%
where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$ \citep[e.g.][]{Arellano-2010}.

@@

Since the RV variation displayed in Fig.~\ref{fig:faculae} is caused by only stellar activity, in this case a faculae, \xavier{we applied the activity correction proposed in Eq.~\ref{eq:RV:correction} to check its efficiency in the case of a faculae.} The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
It is straightforward to see that the proposed correction for \xavier{stellar activity is able to account for the majority of the activity signal created by a faculae, with a $R^2$ of our model larger than 0.95. In addition, the rms of the different estimates of the RV reduces from about 3 \ms before correction to values below 0.15 \ms after correction.
We see a slightly smaller rms after correction for the SN parameters, however the different is not significant. When comparing the correction proposed in Eq.~\ref{eq:RV:correction} with what is generally used, i.e. a linear combination of the asymmetry and width parameter, we see that the proposed correction is able to reduce the rms of the RV residuals by a factor of 2. Looking at the significance of the coefficients in table \ref{table:faculae.test}, we observe that the \umberto{parameter related to the} intercept, $\beta_0$, is only significant at a level of 1\% in the case of the Normal parameters \umberto{or when SN median RV is used}.}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{\umberto{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The new correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
    \label{fig:faculae.correction}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.033$    & $0.00020$ & $0.61$ \\
\hline
$\beta_{1}$            &    $2.22e-16 $    & $2.22e-16 $ & $2.22e-16 $ \\
\hline
$\beta_{2}$            &     $0.0034$   &  $2.22e-16 $ & $2.22e-16 $\\
\hline
$\beta_{3}$            &     $0.00016$   &  $1.091e-6$ & $9.75e-7$\\
\hline
$\beta_{4}$            &     $2.22e-16$   &  $2.22e-16$ & $2.22e-16$\\
\hline
$R^{2}$      &     $0.9978$    &  $0.9985$ & $0.9981$  \\
\hline
\end{tabular}
\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a \textbf{faculae}, according to Eq.~\ref{eq:RV:correction}. All the variables, except the intercept when the independent variable is SN median RV, are statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
\label{table:faculae.test}
\end{table}

@@

As before, we corrected the originally RV's by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction}. Also in this case the proposed correction almost completely addresses the issue when considering the SN or Normal parameters, with values of $R^2$ larger than 0.99. \xavier{Looking at Fig.~\ref{fig:spot.correction}, we see that the activity correction proposed here is able to reduce the signal of a spot from a raw RV rms larger than 4.80\ms down to a rms of 0.38 \ms. In this case the RV rms of the residuals obtained in the case of the Normal parameters is smaller, however,} \xavier{REDO WITH FINAL PLOT with a difference of 6\,$mm.s^{-1}$, we cannot say that this difference is significant. When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear dependance with the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by a factor of 3.5, which is even more than the factor 2 found in the case of the faculae.

In terms of the significance of the different parameters in Eq.~\ref{eq:RV:correction}, summmurized in Table \ref{table:spot.test}, \umberto{we observe that the $\beta_0$, and $\beta_3$, corresponding respectively to the intercept and to the width of the CCF}, are \umberto{not helpful} to understand the variation measured in RV's. This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}. We see also that the ampltitude parameter, with coefficient $\beta_1$ is only useful to explain the RV variation of the spot in the case of the Normal distribution.}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{\umberto{Set of  spurious variations in RV's caused by a \textbf{spot} using a Normal and a SN fit before and once corrected from stellar activity. The new correction has done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity using the proposed linear function (black dots), the residuals present a smaller systematic component if compared with the residuals obtained with the usual correction (blue triangles).}}
    \label{fig:spot.correction}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.4975$    & $0.21$ & $0.21$ \\
\hline
$\beta_{1}$            &    $2e-16$    & $2e-16$ & $2e-16$ \\
\hline
$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.017$   &  $0.13$ & $0.11$\\
\hline
$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$R^{2}$      &     $0.9959$    &  $0.9936$ & $0.9952$  \\
\hline
\end{tabular}
\caption{\umberto{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}. All the covariates are statistically useful to explain the variability in RV's caused by a spot, except the intercept and the width of the CCF. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}}
\label{table:spot.test}
\end{table}

@@

In order to correct the RV's from the spurious variation caused by the spot, \xavier{we need to add to our model of activity correction, a signal to take into account the RV variation caused by the injected planet. The observed RV can therefore be modeled by a combination of the activity and the planet signal:}
%
\begin{equation}
RV= RV_{\text{stellar activity}} + RV_{\text{planet}},
\label{eq:RV:correction.overall}
\end{equation}
%
\xavier{where $RV_{\text{stellar activity}}$ can be found in Eq.~\ref{eq:RV:correction}, and $RV_{\text{planet}}$, in the case of no eccentricity, can be modelled by the following sinusoidal function:}
%
\begin{equation}
RV_{\text{exoplanet}}= K \sin \left(\frac{2 \pi}{P} (t - t_{0})\right),
\label{eq:RV:correction.planet}
\end{equation}
%
where the amplitude $K$, the orbital period $P$ and the epoch at the periapsis $t_{0}$ are three unknown parameters that define the planetary orbit.

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & N mean RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.00063$    & $2e-16$  & $1.42e-09$ \\
\hline
$\beta_{1}$            &    $2e-16$    & $2e-16$  & $2e-16$ \\
\hline
$\beta_{2}$            &     $2e-16$   & $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.067$   &  $0.40$  & $0.38$\\
\hline
$\beta_{4}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
K            &     $2e-16$   &  $2e-16$   & $2e-16$ \\
\hline
P            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
\hline
$t_{0}$            &     $2e-16$   &  $2e-16$ & $2e-16$ \\
\hline
$\text{Residuals}$      &     $0.71 \ms$    &  $ 0.66 \ms$ & $0.70 \ms$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's, according to Eq.~\ref{eq:RV:correction.overall}. All the parameters are statistically helpful to address spurious variations in RV's except the FWHM. Concerning the keplerian parameters, the amplitude $K$ that provides relevance about the possibly presence of the exoplanet. Note that since non linear least squares are required, the residual standard error rather than the $R^2$ is displayed for each case.}
\label{table:spotplanet.test}
\end{table}

@@

\umberto{Do we need to point out the following: \\ If we look at the $R^2$, the proposed function that corrects from stellar activity addresses (almost) all the spurious variations caused in RV's by active regions. Anyway, if we look the residuals, a systematic component is still present, although smaller respect the residual obtained with the usual correction. The residuals are supposed to be homoscedastic with 0 mean under the assumption that the model is correct. Therefore, since our $R^2$ is always close to $1$, we can argue, as we discussed already many times, that the CCF does not follow a normal fit, neither a SN one, otherwise, given our extremely high $R^2$ we should have gotten homoscedastic 0 mean residuals.}
